Evidence of widspread maintenence of functional composition in vertebrate communities

### 2021-09-08 paper/manuscript.Rmd
Update caption

```{r taxa-map, fig.cap="Map of timeseries locations with points color corresponding to taxa.", echo=FALSE}
knitr::include_graphics(here::here("figures/study_map_hist.jpeg"))
```

>>>>

```{r taxa-map, fig.cap="A) Map of timeseries locations with points colored by taxa, and B) histograms of timeseries duration broken down by taxa.", echo=FALSE}
knitr::include_graphics(here::here("figures/study_map_hist.jpeg"))
```
